Evaluating Model Performances

### 2019-05-09 Scripts/evaluating_model_performances.Rmd
editted results script

#Barplots of performance metrics for models

## GM12878

###10kb

```{r}
#OC
##None
rfperf_gm12878_10kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OC/ENET/RF/rfperf.rds")

##RUS
rfperf_gm12878_10kb_rus_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")

##ROS
rfperf_gm12878_10kb_ros_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")

##SMOTE
rfperf_gm12878_10kb_smote_oc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")

#OP
##None
rfperf_gm12878_10kb_none_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/OP/ENET/RF/rfperf.rds")

##RUS
rfperf_gm12878_10kb_rus_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")

##ROS
rfperf_gm12878_10kb_ros_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")

##SMOTE
rfperf_gm12878_10kb_smote_op <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")

#Distance
##None
rfperf_gm12878_10kb_none_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")

##RUS
rfperf_gm12878_10kb_rus_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")

##ROS
rfperf_gm12878_10kb_ros_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")

##SMOTE
rfperf_gm12878_10kb_smote_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

all_rfperfs_gm12878_10kb <- data.frame(Resampling=c(rep("None", 18),
                                       rep("RUS", 18),
                                       rep("ROS", 18),
                                       rep("SMOTE", 18)),
                          Predictor=rep(c(rep("OC", 6),
                                      rep("OP", 6),
                                      rep("Distance", 6)),4),
                          Metric=rep(c("Accuracy", 
                                       "AUPRC", 
                                       "F1-Score", 
                                       "MCC",
                                       "Informedness",
                                       "Balanced Acc"), 12))

all_rfperfs_gm12878_10kb$Performance <- c(round(rfperf_gm12878_10kb_none_oc[9,2],2), #accuracy
                                round(rfperf_gm12878_10kb_none_oc[19,2],2), #auprc
                                round(rfperf_gm12878_10kb_none_oc[16,2],2), #f1
                                round(rfperf_gm12878_10kb_none_oc[15,2],2), #mcc
								round(rfperf_gm12878_10kb_none_oc[18,2],2), #youden
								(round(rfperf_gm12878_10kb_none_oc[6,2],2) + round(rfperf_gm12878_10kb_none_oc[7,2],2))/2, #balanced accuracy

                                round(rfperf_gm12878_10kb_none_op[9,2],2), #accuracy
                                round(rfperf_gm12878_10kb_none_op[19,2],2), #auprc
                                round(rfperf_gm12878_10kb_none_op[16,2],2), #f1
                                round(rfperf_gm12878_10kb_none_op[15,2],2), #mcc
								round(rfperf_gm12878_10kb_none_op[18,2],2), #youden
								(round(rfperf_gm12878_10kb_none_op[6,2],2) + round(rfperf_gm12878_10kb_none_op[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_10kb_none_dist[9,2],2), #accuracy
                                round(rfperf_gm12878_10kb_none_dist[19,2],2), #auprc
                                round(rfperf_gm12878_10kb_none_dist[16,2],2), #f1
                                round(rfperf_gm12878_10kb_none_dist[15,2],2), #mcc
								round(rfperf_gm12878_10kb_none_dist[18,2],2), #youden
								(round(rfperf_gm12878_10kb_none_dist[6,2],2) + round(rfperf_gm12878_10kb_none_dist[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_10kb_rus_oc[9,2],2), #accuracy
                                round(rfperf_gm12878_10kb_rus_oc[19,2],2), #auprc
                                round(rfperf_gm12878_10kb_rus_oc[16,2],2), #f1
                                round(rfperf_gm12878_10kb_rus_oc[15,2],2), #mcc
								round(rfperf_gm12878_10kb_rus_oc[18,2],2), #youden
								(round(rfperf_gm12878_10kb_rus_oc[6,2],2) + round(rfperf_gm12878_10kb_rus_oc[7,2],2))/2, #balanced accuracy

                                round(rfperf_gm12878_10kb_rus_op[9,2],2), #accuracy
                                round(rfperf_gm12878_10kb_rus_op[19,2],2), #auprc
                                round(rfperf_gm12878_10kb_rus_op[16,2],2), #f1
                                round(rfperf_gm12878_10kb_rus_op[15,2],2), #mcc
								round(rfperf_gm12878_10kb_rus_op[18,2],2), #youden
								(round(rfperf_gm12878_10kb_rus_op[6,2],2) + round(rfperf_gm12878_10kb_rus_op[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_10kb_rus_dist[9,2],2), #accuracy
                                round(rfperf_gm12878_10kb_rus_dist[19,2],2), #auprc
                                round(rfperf_gm12878_10kb_rus_dist[16,2],2), #f1
                                round(rfperf_gm12878_10kb_rus_dist[15,2],2), #mcc
								round(rfperf_gm12878_10kb_rus_dist[18,2],2), #youden
								(round(rfperf_gm12878_10kb_rus_dist[6,2],2) + round(rfperf_gm12878_10kb_rus_dist[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_10kb_ros_oc[9,2],2), #accuracy
                                round(rfperf_gm12878_10kb_ros_oc[19,2],2), #auprc
                                round(rfperf_gm12878_10kb_ros_oc[16,2],2), #f1
                                round(rfperf_gm12878_10kb_ros_oc[15,2],2), #mcc
								round(rfperf_gm12878_10kb_ros_oc[18,2],2), #youden
								(round(rfperf_gm12878_10kb_ros_oc[6,2],2) + round(rfperf_gm12878_10kb_ros_oc[7,2],2))/2, #balanced accuracy

                                round(rfperf_gm12878_10kb_ros_op[9,2],2), #accuracy
                                round(rfperf_gm12878_10kb_ros_op[19,2],2), #auprc
                                round(rfperf_gm12878_10kb_ros_op[16,2],2), #f1
                                round(rfperf_gm12878_10kb_ros_op[15,2],2), #mcc
								round(rfperf_gm12878_10kb_ros_op[18,2],2), #youden
								(round(rfperf_gm12878_10kb_ros_op[6,2],2) + round(rfperf_gm12878_10kb_ros_op[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_10kb_ros_dist[9,2],2), #accuracy
                                round(rfperf_gm12878_10kb_ros_dist[19,2],2), #auprc
                                round(rfperf_gm12878_10kb_ros_dist[16,2],2), #f1
                                round(rfperf_gm12878_10kb_ros_dist[15,2],2), #mcc
								round(rfperf_gm12878_10kb_ros_dist[18,2],2), #youden
								(round(rfperf_gm12878_10kb_ros_dist[6,2],2) + round(rfperf_gm12878_10kb_ros_dist[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_10kb_smote_oc[9,2],2), #accuracy
                                round(rfperf_gm12878_10kb_smote_oc[19,2],2), #auprc
                                round(rfperf_gm12878_10kb_smote_oc[16,2],2), #f1
                                round(rfperf_gm12878_10kb_smote_oc[15,2],2), #mcc
								round(rfperf_gm12878_10kb_smote_oc[18,2],2), #youden
								(round(rfperf_gm12878_10kb_smote_oc[6,2],2) + round(rfperf_gm12878_10kb_smote_oc[7,2],2))/2, #balanced accuracy

                                round(rfperf_gm12878_10kb_smote_op[9,2],2), #accuracy
                                round(rfperf_gm12878_10kb_smote_op[19,2],2), #auprc
                                round(rfperf_gm12878_10kb_smote_op[16,2],2), #f1
                                round(rfperf_gm12878_10kb_smote_op[15,2],2), #mcc
								round(rfperf_gm12878_10kb_smote_op[18,2],2), #youden
								(round(rfperf_gm12878_10kb_smote_op[6,2],2) + round(rfperf_gm12878_10kb_smote_op[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_10kb_smote_dist[9,2],2), #accuracy
                                round(rfperf_gm12878_10kb_smote_dist[19,2],2), #auprc
                                round(rfperf_gm12878_10kb_smote_dist[16,2],2), #f1
                                round(rfperf_gm12878_10kb_smote_dist[15,2],2), #mcc
								round(rfperf_gm12878_10kb_smote_dist[18,2],2), #youden
								(round(rfperf_gm12878_10kb_smote_dist[6,2],2) + round(rfperf_gm12878_10kb_smote_dist[7,2],2))/2 #balanced accuracy
								)
all_rfperfs_gm12878_10kb$Resampling <- factor(all_rfperfs_gm12878_10kb$Resampling, levels=c("None","ROS","RUS","SMOTE"))
all_rfperfs_gm12878_10kb$Predictor <- factor(all_rfperfs_gm12878_10kb$Predictor, levels = c("OC", "OP", "Distance"))
all_rfperfs_gm12878_10kb$Metric <- factor(all_rfperfs_gm12878_10kb$Metric, levels = c("Accuracy",
                                                                                      "AUPRC",
                                                                                      "F1-Score",
                                                                                      "MCC",
                                                                                      "Informedness",
                                                                                      "Balanced Acc"))

#comparing only f1 and mcc and balanced acc

ggplot(all_rfperfs_gm12878_10kb[which(all_rfperfs_gm12878_10kb$Metric=="F1-Score" |
                                               all_rfperfs_gm12878_10kb$Metric=="MCC" |
                                        all_rfperfs_gm12878_10kb$Metric=="Balanced Acc"),],
                       aes(x=Resampling, y=Performance, fill=Predictor)) +
  geom_bar( stat="identity", position="dodge") +
  facet_grid(~ Metric) +
  xlab("Resampling Technique") +
  theme_minimal() +
  theme_bw() +
  scale_fill_discrete(name="Predictor Type")+
  #guides(fill=FALSE)+
	theme(axis.text.x = element_text(size=15,
	                                 angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))

@@

###25kb

```{r}
#OC
##None
rfperf_gm12878_25kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OC/ENET/RF/rfperf.rds")

##RUS
rfperf_gm12878_25kb_rus_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")

##ROS
rfperf_gm12878_25kb_ros_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")

##SMOTE
rfperf_gm12878_25kb_smote_oc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")

#OP
##None
rfperf_gm12878_25kb_none_op <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/OP/ENET/RF/rfperf.rds")

##RUS
rfperf_gm12878_25kb_rus_op <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")

##ROS
rfperf_gm12878_25kb_ros_op <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")

##SMOTE
rfperf_gm12878_25kb_smote_op <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")

#Distance
##None
rfperf_gm12878_25kb_none_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")

##RUS
rfperf_gm12878_25kb_rus_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")

##ROS
rfperf_gm12878_25kb_ros_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")

##SMOTE
rfperf_gm12878_25kb_smote_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

all_rfperfs_gm12878_25kb <- data.frame(Resampling=c(rep("None", 18),
                                       rep("RUS", 18),
                                       rep("ROS", 18),
                                       rep("SMOTE", 18)),
                          Predictor=rep(c(rep("OC", 6),
                                      rep("OP", 6),
                                      rep("Distance", 6)),4),
                          Metric=rep(c("Accuracy", 
                                       "AUPRC", 
                                       "F1-Score", 
                                       "MCC",
                                       "Informedness",
                                       "Balanced Acc"), 12))

all_rfperfs_gm12878_25kb$Performance <- c(round(rfperf_gm12878_25kb_none_oc[9,2],2), #accuracy
                                round(rfperf_gm12878_25kb_none_oc[19,2],2), #auprc
                                round(rfperf_gm12878_25kb_none_oc[16,2],2), #f1
                                round(rfperf_gm12878_25kb_none_oc[15,2],2), #mcc
								round(rfperf_gm12878_25kb_none_oc[18,2],2), #youden
								(round(rfperf_gm12878_25kb_none_oc[6,2],2) + round(rfperf_gm12878_25kb_none_oc[7,2],2))/2, #balanced accuracy

                                round(rfperf_gm12878_25kb_none_op[9,2],2), #accuracy
                                round(rfperf_gm12878_25kb_none_op[19,2],2), #auprc
                                round(rfperf_gm12878_25kb_none_op[16,2],2), #f1
                                round(rfperf_gm12878_25kb_none_op[15,2],2), #mcc
								round(rfperf_gm12878_25kb_none_op[18,2],2), #youden
								(round(rfperf_gm12878_25kb_none_op[6,2],2) + round(rfperf_gm12878_25kb_none_op[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_25kb_none_dist[9,2],2), #accuracy
                                round(rfperf_gm12878_25kb_none_dist[19,2],2), #auprc
                                round(rfperf_gm12878_25kb_none_dist[16,2],2), #f1
                                round(rfperf_gm12878_25kb_none_dist[15,2],2), #mcc
								round(rfperf_gm12878_25kb_none_dist[18,2],2), #youden
								(round(rfperf_gm12878_25kb_none_dist[6,2],2) + round(rfperf_gm12878_25kb_none_dist[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_25kb_rus_oc[9,2],2), #accuracy
                                round(rfperf_gm12878_25kb_rus_oc[19,2],2), #auprc
                                round(rfperf_gm12878_25kb_rus_oc[16,2],2), #f1
                                round(rfperf_gm12878_25kb_rus_oc[15,2],2), #mcc
								round(rfperf_gm12878_25kb_rus_oc[18,2],2), #youden
								(round(rfperf_gm12878_25kb_rus_oc[6,2],2) + round(rfperf_gm12878_25kb_rus_oc[7,2],2))/2, #balanced accuracy

                                round(rfperf_gm12878_25kb_rus_op[9,2],2), #accuracy
                                round(rfperf_gm12878_25kb_rus_op[19,2],2), #auprc
                                round(rfperf_gm12878_25kb_rus_op[16,2],2), #f1
                                round(rfperf_gm12878_25kb_rus_op[15,2],2), #mcc
								round(rfperf_gm12878_25kb_rus_op[18,2],2), #youden
								(round(rfperf_gm12878_25kb_rus_op[6,2],2) + round(rfperf_gm12878_25kb_rus_op[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_25kb_rus_dist[9,2],2), #accuracy
                                round(rfperf_gm12878_25kb_rus_dist[19,2],2), #auprc
                                round(rfperf_gm12878_25kb_rus_dist[16,2],2), #f1
                                round(rfperf_gm12878_25kb_rus_dist[15,2],2), #mcc
								round(rfperf_gm12878_25kb_rus_dist[18,2],2), #youden
								(round(rfperf_gm12878_25kb_rus_dist[6,2],2) + round(rfperf_gm12878_25kb_rus_dist[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_25kb_ros_oc[9,2],2), #accuracy
                                round(rfperf_gm12878_25kb_ros_oc[19,2],2), #auprc
                                round(rfperf_gm12878_25kb_ros_oc[16,2],2), #f1
                                round(rfperf_gm12878_25kb_ros_oc[15,2],2), #mcc
								round(rfperf_gm12878_25kb_ros_oc[18,2],2), #youden
								(round(rfperf_gm12878_25kb_ros_oc[6,2],2) + round(rfperf_gm12878_25kb_ros_oc[7,2],2))/2, #balanced accuracy

                                round(rfperf_gm12878_25kb_ros_op[9,2],2), #accuracy
                                round(rfperf_gm12878_25kb_ros_op[19,2],2), #auprc
                                round(rfperf_gm12878_25kb_ros_op[16,2],2), #f1
                                round(rfperf_gm12878_25kb_ros_op[15,2],2), #mcc
								round(rfperf_gm12878_25kb_ros_op[18,2],2), #youden
								(round(rfperf_gm12878_25kb_ros_op[6,2],2) + round(rfperf_gm12878_25kb_ros_op[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_25kb_ros_dist[9,2],2), #accuracy
                                round(rfperf_gm12878_25kb_ros_dist[19,2],2), #auprc
                                round(rfperf_gm12878_25kb_ros_dist[16,2],2), #f1
                                round(rfperf_gm12878_25kb_ros_dist[15,2],2), #mcc
								round(rfperf_gm12878_25kb_ros_dist[18,2],2), #youden
								(round(rfperf_gm12878_25kb_ros_dist[6,2],2) + round(rfperf_gm12878_25kb_ros_dist[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_25kb_smote_oc[9,2],2), #accuracy
                                round(rfperf_gm12878_25kb_smote_oc[19,2],2), #auprc
                                round(rfperf_gm12878_25kb_smote_oc[16,2],2), #f1
                                round(rfperf_gm12878_25kb_smote_oc[15,2],2), #mcc
								round(rfperf_gm12878_25kb_smote_oc[18,2],2), #youden
								(round(rfperf_gm12878_25kb_smote_oc[6,2],2) + round(rfperf_gm12878_25kb_smote_oc[7,2],2))/2, #balanced accuracy

                                round(rfperf_gm12878_25kb_smote_op[9,2],2), #accuracy
                                round(rfperf_gm12878_25kb_smote_op[19,2],2), #auprc
                                round(rfperf_gm12878_25kb_smote_op[16,2],2), #f1
                                round(rfperf_gm12878_25kb_smote_op[15,2],2), #mcc
								round(rfperf_gm12878_25kb_smote_op[18,2],2), #youden
								(round(rfperf_gm12878_25kb_smote_op[6,2],2) + round(rfperf_gm12878_25kb_smote_op[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_25kb_smote_dist[9,2],2), #accuracy
                                round(rfperf_gm12878_25kb_smote_dist[19,2],2), #auprc
                                round(rfperf_gm12878_25kb_smote_dist[16,2],2), #f1
                                round(rfperf_gm12878_25kb_smote_dist[15,2],2), #mcc
								round(rfperf_gm12878_25kb_smote_dist[18,2],2), #youden
								(round(rfperf_gm12878_25kb_smote_dist[6,2],2) + round(rfperf_gm12878_25kb_smote_dist[7,2],2))/2 #balanced accuracy
								)
all_rfperfs_gm12878_25kb$Resampling <- factor(all_rfperfs_gm12878_25kb$Resampling, levels=c("None","ROS","RUS","SMOTE"))
all_rfperfs_gm12878_25kb$Predictor <- factor(all_rfperfs_gm12878_25kb$Predictor, levels = c("OC", "OP", "Distance"))
all_rfperfs_gm12878_25kb$Metric <- factor(all_rfperfs_gm12878_25kb$Metric, levels = c("Accuracy",
                                                                                      "AUPRC",
                                                                                      "F1-Score",
                                                                                      "MCC",
                                                                                      "Informedness",
                                                                                      "Balanced Acc"))

#comparing only f1 and mcc and balanced acc

ggplot(all_rfperfs_gm12878_25kb[which(all_rfperfs_gm12878_25kb$Metric=="F1-Score" |
                                               all_rfperfs_gm12878_25kb$Metric=="MCC" |
                                        all_rfperfs_gm12878_25kb$Metric=="Balanced Acc"),],
                       aes(x=Resampling, y=Performance, fill=Predictor)) +
  geom_bar( stat="identity", position="dodge") +
  facet_grid(~ Metric) +
  xlab("Resampling Technique") +
  theme_minimal() +
  theme_bw() +
  scale_fill_discrete(name="Predictor Type")+
  #guides(fill=FALSE)+
	theme(axis.text.x = element_text(size=15,
	                                 angle = 45, 
                                   #margin = ggplot2::margin(t = 35),
                                   hjust = 1),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20))

@@

###50kb

```{r}
#OC
##None
rfperf_gm12878_50kb_none_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OC/ENET/RF/rfperf.rds")

##RUS
rfperf_gm12878_50kb_rus_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OC/ENET/RF/rfperf.rds")

##ROS
rfperf_gm12878_50kb_ros_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OC/ENET/RF/rfperf.rds")

##SMOTE
rfperf_gm12878_50kb_smote_oc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OC/ENET/RF/rfperf.rds")

#OP
##None
rfperf_gm12878_50kb_none_op <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/OP/ENET/RF/rfperf.rds")

##RUS
rfperf_gm12878_50kb_rus_op <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/OP/ENET/RF/rfperf.rds")

##ROS
rfperf_gm12878_50kb_ros_op <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/OP/ENET/RF/rfperf.rds")

##SMOTE
rfperf_gm12878_50kb_smote_op <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/OP/ENET/RF/rfperf.rds")

#Distance
##None
rfperf_gm12878_50kb_none_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/None/Distance/ENET/RF/rfperf.rds")

##RUS
rfperf_gm12878_50kb_rus_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/RUS/Distance/ENET/RF/rfperf.rds")

##ROS
rfperf_gm12878_50kb_ros_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/ROS/Distance/ENET/RF/rfperf.rds")

##SMOTE
rfperf_gm12878_50kb_smote_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/SMOTE/Distance/ENET/RF/rfperf.rds")

all_rfperfs_gm12878_50kb <- data.frame(Resampling=c(rep("None", 18),
                                       rep("RUS", 18),
                                       rep("ROS", 18),
                                       rep("SMOTE", 18)),
                          Predictor=rep(c(rep("OC", 6),
                                      rep("OP", 6),
                                      rep("Distance", 6)),4),
                          Metric=rep(c("Accuracy", 
                                       "AUPRC", 
                                       "F1-Score", 
                                       "MCC",
                                       "Informedness",
                                       "Balanced Acc"), 12))

all_rfperfs_gm12878_50kb$Performance <- c(round(rfperf_gm12878_50kb_none_oc[9,2],2), #accuracy
                                round(rfperf_gm12878_50kb_none_oc[19,2],2), #auprc
                                round(rfperf_gm12878_50kb_none_oc[16,2],2), #f1
                                round(rfperf_gm12878_50kb_none_oc[15,2],2), #mcc
								round(rfperf_gm12878_50kb_none_oc[18,2],2), #youden
								(round(rfperf_gm12878_50kb_none_oc[6,2],2) + round(rfperf_gm12878_50kb_none_oc[7,2],2))/2, #balanced accuracy

                                round(rfperf_gm12878_50kb_none_op[9,2],2), #accuracy
                                round(rfperf_gm12878_50kb_none_op[19,2],2), #auprc
                                round(rfperf_gm12878_50kb_none_op[16,2],2), #f1
                                round(rfperf_gm12878_50kb_none_op[15,2],2), #mcc
								round(rfperf_gm12878_50kb_none_op[18,2],2), #youden
								(round(rfperf_gm12878_50kb_none_op[6,2],2) + round(rfperf_gm12878_50kb_none_op[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_50kb_none_dist[9,2],2), #accuracy
                                round(rfperf_gm12878_50kb_none_dist[19,2],2), #auprc
                                round(rfperf_gm12878_50kb_none_dist[16,2],2), #f1
                                round(rfperf_gm12878_50kb_none_dist[15,2],2), #mcc
								round(rfperf_gm12878_50kb_none_dist[18,2],2), #youden
								(round(rfperf_gm12878_50kb_none_dist[6,2],2) + round(rfperf_gm12878_50kb_none_dist[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_50kb_rus_oc[9,2],2), #accuracy
                                round(rfperf_gm12878_50kb_rus_oc[19,2],2), #auprc
                                round(rfperf_gm12878_50kb_rus_oc[16,2],2), #f1
                                round(rfperf_gm12878_50kb_rus_oc[15,2],2), #mcc
								round(rfperf_gm12878_50kb_rus_oc[18,2],2), #youden
								(round(rfperf_gm12878_50kb_rus_oc[6,2],2) + round(rfperf_gm12878_50kb_rus_oc[7,2],2))/2, #balanced accuracy

                                round(rfperf_gm12878_50kb_rus_op[9,2],2), #accuracy
                                round(rfperf_gm12878_50kb_rus_op[19,2],2), #auprc
                                round(rfperf_gm12878_50kb_rus_op[16,2],2), #f1
                                round(rfperf_gm12878_50kb_rus_op[15,2],2), #mcc
								round(rfperf_gm12878_50kb_rus_op[18,2],2), #youden
								(round(rfperf_gm12878_50kb_rus_op[6,2],2) + round(rfperf_gm12878_50kb_rus_op[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_50kb_rus_dist[9,2],2), #accuracy
                                round(rfperf_gm12878_50kb_rus_dist[19,2],2), #auprc
                                round(rfperf_gm12878_50kb_rus_dist[16,2],2), #f1
                                round(rfperf_gm12878_50kb_rus_dist[15,2],2), #mcc
								round(rfperf_gm12878_50kb_rus_dist[18,2],2), #youden
								(round(rfperf_gm12878_50kb_rus_dist[6,2],2) + round(rfperf_gm12878_50kb_rus_dist[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_50kb_ros_oc[9,2],2), #accuracy
                                round(rfperf_gm12878_50kb_ros_oc[19,2],2), #auprc
                                round(rfperf_gm12878_50kb_ros_oc[16,2],2), #f1
                                round(rfperf_gm12878_50kb_ros_oc[15,2],2), #mcc
								round(rfperf_gm12878_50kb_ros_oc[18,2],2), #youden
								(round(rfperf_gm12878_50kb_ros_oc[6,2],2) + round(rfperf_gm12878_50kb_ros_oc[7,2],2))/2, #balanced accuracy

                                round(rfperf_gm12878_50kb_ros_op[9,2],2), #accuracy
                                round(rfperf_gm12878_50kb_ros_op[19,2],2), #auprc
                                round(rfperf_gm12878_50kb_ros_op[16,2],2), #f1
                                round(rfperf_gm12878_50kb_ros_op[15,2],2), #mcc
								round(rfperf_gm12878_50kb_ros_op[18,2],2), #youden
								(round(rfperf_gm12878_50kb_ros_op[6,2],2) + round(rfperf_gm12878_50kb_ros_op[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_50kb_ros_dist[9,2],2), #accuracy
                                round(rfperf_gm12878_50kb_ros_dist[19,2],2), #auprc
                                round(rfperf_gm12878_50kb_ros_dist[16,2],2), #f1
                                round(rfperf_gm12878_50kb_ros_dist[15,2],2), #mcc
								round(rfperf_gm12878_50kb_ros_dist[18,2],2), #youden
								(round(rfperf_gm12878_50kb_ros_dist[6,2],2) + round(rfperf_gm12878_50kb_ros_dist[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_50kb_smote_oc[9,2],2), #accuracy
                                round(rfperf_gm12878_50kb_smote_oc[19,2],2), #auprc
                                round(rfperf_gm12878_50kb_smote_oc[16,2],2), #f1
                                round(rfperf_gm12878_50kb_smote_oc[15,2],2), #mcc
								round(rfperf_gm12878_50kb_smote_oc[18,2],2), #youden
								(round(rfperf_gm12878_50kb_smote_oc[6,2],2) + round(rfperf_gm12878_50kb_smote_oc[7,2],2))/2, #balanced accuracy

                                round(rfperf_gm12878_50kb_smote_op[9,2],2), #accuracy
                                round(rfperf_gm12878_50kb_smote_op[19,2],2), #auprc
                                round(rfperf_gm12878_50kb_smote_op[16,2],2), #f1
                                round(rfperf_gm12878_50kb_smote_op[15,2],2), #mcc
								round(rfperf_gm12878_50kb_smote_op[18,2],2), #youden
								(round(rfperf_gm12878_50kb_smote_op[6,2],2) + round(rfperf_gm12878_50kb_smote_op[7,2],2))/2, #balanced accuracy

								round(rfperf_gm12878_50kb_smote_dist[9,2],2), #accuracy
                                round(rfperf_gm12878_50kb_smote_dist[19,2],2), #auprc
                                round(rfperf_gm12878_50kb_smote_dist[16,2],2), #f1
                                round(rfperf_gm12878_50kb_smote_dist[15,2],2), #mcc
								round(rfperf_gm12878_50kb_smote_dist[18,2],2), #youden
								(round(rfperf_gm12878_50kb_smote_dist[6,2],2) + round(rfperf_gm12878_50kb_smote_dist[7,2],2))/2 #balanced accuracy
								)
all_rfperfs_gm12878_50kb$Resampling <- factor(all_rfperfs_gm12878_50kb$Resampling, levels=c("None","ROS","RUS","SMOTE"))
all_rfperfs_gm12878_50kb$Predictor <- factor(all_rfperfs_gm12878_50kb$Predictor, levels = c("OC", "OP", "Distance"))
all_rfperfs_gm12878_50kb$Metric <- factor(all_rfperfs_gm12878_50kb$Metric, levels = c("Accuracy",
                                                                                      "AUPRC",
                                                                                      "F1-Score",
                                                                                      "MCC",
                                                                                      "Informedness",
                                                                                      "Balanced Acc"))

#comparing only f1 and mcc and balanced acc

>>>>

# GM12878

##10kb

```{r}
mccdata_gm12878_10kb <- numeric()

for(i in paste0("CHR", c(1:8,10:22))){
	for(j in c("none","ros","rus","smote")){
		for(k in c("distance", "oc", "op")){
			perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
									   i, 
									   "/",
									   j, 
									   "/", 
									   k, 
									   "/enet/rfperf.rds"))

			mccdata_gm12878_10kb <- rbind(mccdata_gm12878_10kb,
										  perfdata[15,2])
		}
	}
}

@@

##25kb

```{r}
mccdata_gm12878_25kb <- numeric()

for(i in paste0("CHR", c(1:8,10:22))){
	for(j in c("none","ros","rus","smote")){
		for(k in c("distance", "oc", "op")){
			perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/",
									   i, 
									   "/",
									   j, 
									   "/", 
									   k, 
									   "/enet/rfperf.rds"))

			mccdata_gm12878_25kb <- rbind(mccdata_gm12878_25kb,
										  perfdata[15,2])
		}
	}
}

@@

##50kb

```{r}
mccdata_gm12878_50kb <- numeric()

for(i in paste0("CHR", c(1:8,10:22))){
	for(j in c("none","ros","rus","smote")){
		for(k in c("distance", "oc", "op")){
			perfdata <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/50kb/results_by_chr/",
									   i, 
									   "/",
									   j, 
									   "/", 
									   k, 
									   "/enet/rfperf.rds"))

			mccdata_gm12878_50kb <- rbind(mccdata_gm12878_50kb,
										  perfdata[15,2])
		}
	}
}
